Document knowledge base linking for information retrieval

### 2016-02-12 paper.tex
added AP stanbol results

\begin{table}[htbp]
\centering
\begin{tabular}{|c|l|c|c|} \hline
& {\bf Run} & {\bf $\lambda$} & {\bf MAP} \\ \hline
\multirow{3}{*}{Robust} & {\it baseline-ql} & -- & 0.2183 \\ \cline{2-4}
& {\it kb-ql} & 0.9 & {\bf 0.2275} \\ \cline{2-4}
& {\it stanbol-ql} & 0.1 & 0.1928 \\ \hline \hline 
\multirow{3}{*}{AP} & {\it baseline-ql} & -- & 0.2346 \\ \cline{2-4}
& {\it kb-ql} & 0.9 & {\bf 0.2515} \\ \cline{2-4}
& {\it stanbol-ql} & 0.1 &  \\ \hline
\end{tabular}
\caption{The top-scoring runs and baselines by MAP. Bolded values indicate statistically significant improvements.}
\label{table.performance}
\end{table}

\begin{figure}
\centering
\begin{subfigure}{.5\columnwidth}
\centering
\includegraphics[width=\textwidth]{figures/sweep-ql.pdf}
\end{subfigure}%
\begin{subfigure}{.5\columnwidth}
\centering
\includegraphics[width=\textwidth]{figures/sweep-stanbol.pdf}
\end{subfigure}
\caption{Sweeps over values of $\lambda$ for robust (red) and AP (blue) for (a) \textit{kb} and (b) \textit{stanbol} runs.}
\label{figure.sweeps-ql}
\end{figure}

>>>>

\begin{table}[htbp]
\centering
\begin{tabular}{|c|l|c|c|} \hline
& {\bf Run} & {\bf $\lambda$} & {\bf MAP} \\ \hline
\multirow{3}{*}{Robust} & {\it baseline-ql} & -- & 0.2183 \\ \cline{2-4}
& {\it kb-ql} & 0.9 & {\bf 0.2275} \\ \cline{2-4}
& {\it stanbol-ql} & 0.1 & 0.1928 \\ \hline \hline 
\multirow{3}{*}{AP} & {\it baseline-ql} & -- & 0.2346 \\ \cline{2-4}
& {\it kb-ql} & 0.9 & {\bf 0.2515} \\ \cline{2-4}
& {\it stanbol-ql} & 0.1 & 0.1951 \\ \hline
\end{tabular}
\caption{The top-scoring runs and baselines by MAP. Bolded values indicate statistically significant improvements.}
\label{table.performance}
\end{table}

\begin{figure}
\centering
\begin{subfigure}{.5\columnwidth}
\centering
\includegraphics[width=\textwidth]{figures/sweep-ql.pdf}
\end{subfigure}%
\begin{subfigure}{.5\columnwidth}
\centering
\includegraphics[width=\textwidth]{figures/sweep-stanbol.pdf}
\end{subfigure}
\caption{Sweeps over values of $\lambda$ for robust (red) and AP (blue) for \textit{kb} (a) and \textit{stanbol} (b) runs.}
\label{figure.sweeps-ql}
\end{figure}
